Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-12-07 papers/integration/omm_integ.tex
Changes to discussion  additions after talking to Kevin, results of lit search for variable weights in STT

% Brain to SBG, seeing as that's how I explained it above.
A number of studies have considered the form of the connection between
the deeper layers of the superior colliculus and the saccadic burst
generator \citep{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_two-dimensional_1994,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
which has become known as the spatial temporal transform (STT).  The
spatial aspect of the transform is thought to be implemented by a
weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994}
and we follow this idea.
%
Arai and co-workers trained a 20x20 neural network model of the
superior colliculus to discover the weight map under the assumption of
2D Gaussian activation
profiles~\citep{arai_two-dimensional_1994}---\rvwt{that is, they
assumed that the activity in superior colliculus for any saccade was a
size-invariant 2D Gaussian hill of activity}.
%
The training approach of \cite{arai_two-dimensional_1994} was not
feasible in this study due to the length of time required to run our
model and its stochasticity, which meant multiple runs of the model
were necessary in order to generate output statistics.
%
\cite{tabareau_geometry_2007} wrote down a theoretical form of the weight
map, \rvwt{obtained by inverting the mapping} of \cite{ottes_visuomotor_1986}
and the assumption of invariant 2D Gaussian activity profiles in SC,
\rvwt{which is equivalent to:}
%
\begin{equation} \label{eq:tabareau_eq3}
w(r,\phi) = i\;e\,^{jr}\;\sin\left(l\phi + k\right)
\end{equation}
\rvwt{where $r$ and $\phi$ are co-ordinates on the collicular map and
$i$, $j$, $k$ and $l$ are parameters of the
function (compare with Eq.~3 of \cite{tabareau_geometry_2007}).}
%
As they found it closely resembles the results
of \cite{arai_two-dimensional_1994}, and it is a simple formulation,
we considered it as the means to generate the six weight maps in our
own model.
%
One barrier to the use of this weight map was the \ccg~model's
violation of the
\e{invariant integral hypothesis}. This states that the number of spikes
emitted by a neural element during a saccade (or in our model, the
integral of the neuron's output during the saccade) should be a
function only of its position within the hill of collicular
activity. That is, for any time-dependent hill of activity
$\mathcal{A}(\mathbf{z},t)$ at $\mathbf{z} = (r,\phi)$ on the collicular
surface, the integrated activity  $A_{\mathbf{x}}$ in an element at a
vector $\mathbf{x}$ away from $\mathbf{z}$ is
\begin{equation}
A_{\mathbf{x}} = \int_t \mathcal{A}(\mathbf{z}-\mathbf{x}, t)\;dt
\end{equation}
which is invariant for all $\mathbf{z}$. \rvwt{This requirement is
fulfilled by spatially invariant 2D Gaussian profiles, whose
time-course (how quickly they grow and then diminish) is always the
same.}

@@

A further issue regarding the use of the theoretical weight map
in \cite{tabareau_geometry_2007} was that it does not consider the
existence of the oblique extraocular muscles. There is evidence that
only two dimensional information is encoded in superior
colliculus
\citep{wurtz_activity_1972,hepp_monkey_1993,van_opstal_two-rather_1991},
but the eye is actuated by six extraocular muscles. In order to find
out a possible form for the input to the oblique muscles we carried
out a training process
% possibly descibe this training process in supplemental data
which depended on a centroid computation in SC\_deep. For the four
rectus muscles, the resulting weight maps resembled those found by
\cite{arai_two-dimensional_1994}. The trained
maps for the oblique muscles had a form very close to those for the
inferior and superior rectus channels, but with a smaller magnitude.
The inferior oblique map resembled the superior rectus map and the
superior oblique map resembled the inferior rectus. When parameterising
the theoretical weight maps, we set the inferior/superior
oblique maps to be 1/10$^{\mathrm{th}}$ of the superior/inferior rectus
maps, respectively. Interestingly, this suggests that there is a built-in
synergy between the vertical and oblique channels in the eye, although
the results will show there is some systematic change in the oblique error
with saccade end-point location.

@@

% FIXME: Add reference to weight maps neuroscience if possible.
We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:results:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{fig:saccvstarg}(a) \& \rvw{(b)}. We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$.

The resulting weight maps (where the oblique maps are
1/10$^{\mathrm{th}}$ of the vertical maps, as described earlier) are
shown in Fig.~\ref{fig:weightmaps}.
%
\rvw{First, recall that the $r$ axis of the neural surface corresponds
to the amplitude of a saccade and the $\phi$ axis indicates the polar
direction of the saccade, as described in Sect.~\ref{sec:mapping} and
Fig.~\ref{fig:mapping}. Fig.~\ref{fig:weightmaps}(a) shows the weight map
for the muscle which rotates the eye to the left. As we modelled a
left eye, this actuates the lateral rectus muscle. The exponential
rise of Eq.~\ref{eq:weightmaps} is seen in the $r$ direction; as $r$
increases, so the connection strength to the SBG channel rises
exponentially. The connection strength is greatest along the centre
line, for a value of $\phi$ which corresponds to a purely leftward
movement. Note that $\phi$ is presented in neural coordinates, and not
in degrees or radians; 1$\leq\phi\leq$50 corresponds to a range of
0\dg~to 360\dg; $\phi=$38.5 corresponds to movements left. The
connections strength drops away sinusoidally as $\phi$ moves away from
the centre line at $\phi=$38.5. In regions of the map for which there
is no leftward movement, that is, in the half of the map which
corresponds to any movement with a rightward component, the `left'
weight map is 0. Fig.~\ref{fig:weightmaps}(d) shows the weight map for
rightward movements, actuating the medial rectus muscle of the
eye. The line of maximum connection strength is along $\phi=$13.5. The
map is a mirror of Fig.~\ref{fig:weightmaps}(a), reflected about the line
$\phi$=26. The `left' and `right' weight maps are orthogonal; the
non-zero region of the `left' map is zero in the `right' map and vice
versa. Fig~\ref{fig:weightmaps}(b) \& (d) show the weight maps for
downward and upward eye movements; the `down' map activates the SBG
channel for the inferior rectus muscle, the `up' map activates the
superior rectus. Note that `down' is not orthogonal either to `left'
or `right' because a saccade down and left is achieved by
simultaneously activating both the lateral and inferior rectus
muscles. However, the `up' map \e{is} orthogonal to the `down' map and
spans the edges of the surface where $\phi$ rolls over from 1 to
50. The line of maximum connection strength for the `up' map is along
$\phi=$1; for `down' $\phi=$26. Based on the training described in
Sect.~\ref{sec:methods:integrating}, the maps driving the superior
oblique (`Z+') and inferior oblique (`Z-') muscles were set to
1/10$^{\mathrm{th}}$ of the `down' and `up' maps.}
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

@@

To verify that our implementation of the brain model has the same
functionality as that reported in \cite{cope_basal_2017}, we
investigated the effect on saccadic response times of: target
eccentricity; and any gap or overlap between fixation off-time and
target on-time. We showed that the full model reproduces the `hockey
stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for horizontal
[Fig.~\ref{fig:latvsall}(a)], vertical [Fig.~\ref{fig:latvsall}(b)] and
oblique saccades (not shown). The latency increases with eccentricity
far from the fovea because the retinotopic mapping reduces the
activity in the basal ganglia for more eccentric targets (see
Fig.~\ref{fig:mapping}). Closer to the fovea, the \rvwt{effect of} the
foveal mask \rvwt{on} the activity in FEF again leads to reduced input
into the basal ganglia and an increased time to achieve disinhibition
in SNr.

@@

The aim of this study was to demonstrate the importance of modelling
neurological systems \e{in concert with} the biomechanical systems
with which they have evolved. We hypothesised that by
combining existing neurophysiological models with an accurate model of
a musculo-skeletal system, and then \rvw{closing the
`agent-environment-agent' loop} by allowing the
movements of the virtual muscles to modulate sensory feedback to the
brain model, shortcomings in the constituent models would be revealed,
leading to new knowledge.
%
\rvw{We call this closed-loop approach \e{computational
neurobehaviour}, meaning a complete, behaving model, with attention
paid to the biological accuracy of each brain and biomechanical
sub-system. There already exist many closed-loop \e{robotic} systems which
receive sensory input from the world, process that input and generate
behaviour by activating motor
systems
\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
now consider whether robotic systems which model biological
components \e{in hardware} could fall within our new category.
%
Using a number of examples, we will attempt to illustrate what we mean
by computational neurobehaviour. We'll consider which examples fall
into the new category and which are covered by other fields of
robotics or computational neuroscience.}

\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
biomimetic whisker sensory system, along with a biomimetic neural
system imitating the operation of the rat's sensory processing
and controlling the movement of the robot. \cite{fend_artificial_2004}
is a similar, wheeled, whiskered robot, with a repertoire of three
behaviours organised in a subsumption architecture. In both robots,
actions that are selected within the brain model drive a
non-biologically accurate wheel motor control algorithm to achieve
rotational and translational movements. Although both have
sensory and processing systems which are guided by biology, the
non-biological motor control stage prevents us from considering these
as being studies of computational neurobehaviour.}
%
\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
whose motor system closely resembles that of the real fish. The robot
is able to operate in a closed-loop mode, where sensory input is
provided to the non-biomimetic control algorithms from overhead
cameras, but its control system is also able to operate in open-loop
mode. Neither the control system, nor the sensory system are
biophysically accurate and we would not describe this study as
computational neurobehaviour. Nevertheless, the biophysically accurate
motor system could certainly form part of a computational
neurobehavioural study of swimming behaviour in the fish, if it were
combined with suitable sensory input and sensory processing models.}
%
\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
arm controlled via a dynamic neural field brain model. The sensory
input for this system---its `eyes'---is a Microsoft Kinect sensor; it
also has somatosensory feedback from the fingers of the robot's
hand. The neural field `brain' controls the seven degrees of freedom
of the arm to carry out the reach-and-grasp action. While this robot
has closed-loop control and is clearly inspired by biology, it remains
a study of robotics and of the improvement of the control of the
robot's reach-and-grasp function, rather than a study which aims to
learn more about the biology of a primate arm. For this reason, we
would describe the study of \cite{knips_neural_2017} as embodied
robotics or neuro-robotics.}

\rvw{Modern programming platforms, often originating from the
computer game industry, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuro-mimetic control are carried out with virtual robots
operating within a virtual environment. \cite{arena_motor-skill_2017}
describes a robotic insect system based on the fly
species \e{Drosophila Melanogaster}. It has biomimetic insect legs
implemented in a virtual robot and a neuro-mimetic brain. Closing the
loop is a visual sensory input system which is able to determine the
distance between the robot and an obstacle and the obstacle's
height. The visual system is not described in detail and may not be
biologically modelled (much in the way that the visual processing
stream is not modelled in detail in the present work). Nevertheless,
this study may reasonably be described as compuational neurobehaviour;
the authors demonstrate that the virtual robot is able to learn to
climb obstacles in a realistic manner and suggest that the model may
be compared with experimental data from future Drosophila experiments
addressing obstacle climbing and learning.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control and motor output. These
studies fall outside the remit of computational neurobehaviour only
because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewere degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a traditional
computational neuroscience study.}

\rvw{We can now offer a definition of computational
neurobehaviour as: \e{The study of biological sensory-motor system
behaviour using biophysically accurate models of sensory input, brain
and motor sub-systems operating in a closed-loop}. The sub-system
models may be implemented in software or hardware, provided that they
attempt to reproduce and explain features of the biological
sub-system. We favour virtual biomechanics, for the ease with which
the biomechanical model can be modified and the flexibility of
computational modelling over hardware modelling.}

To demonstrate the validity of the computational neurobehaviour
approach, we built an integrated model and then identified the
modifications which were necessary to give it the ability to make
accurate movements under one type of stimulus. We then examined its
behaviour with other stimuli. We chose the oculomotor model as a basis
for this study because it has only three degrees of freedom, making it
one of the simplest musculo-skeletal systems. Furthermore, eye
movements fall into several well-defined categories, each being
controlled by separate brain circuits, we were therefore justified in
modelling a system which produced only saccadic eye
movements. Nevertheless, we are aware that we did not create a
complete model of the system; no treatment of the cerebellum was
attempted, justified because cerebellum appears to have only a minor
effect on saccade accuracy \citep{dean_adaptive_2008}, probably
correcting for slow to medium timescale changes in the physical
dynamics of the eyeball \citep{dean_learning_1994}.

To summarise our model integration: We combined
the \ccg~model \citep{cope_basal_2017} with a saccadic burst generator
model based on the work of \cite{gancarz_neural_1998}, using this to
drive the input of a new biomechanical eye model. To achieve the
spatial transformation from the retinotopic maps of the \ccg~model to
the six `muscle channel' inputs for the saccadic burst generator, we
used the mapping of \cite{ottes_visuomotor_1986} to produce
parameterised weight maps along with an empirically discovered synergy
for the torsional weight maps. We introduced an additional
transformation to the brain model to achieve invariant sized hills of
activity in superior colliculus to fulfil the invariant integral
hypothesis of \cite{tabareau_geometry_2007}. We closed the loop using
a software component which transformed a view of a world containing
luminous cross shapes into the eye's frame of reference, given its
instantaneous rotational state. This component also computed the
inverse of the mapping from \cite{ottes_visuomotor_1986} to project
the view retinotopically into the brain model.
%
This paper serves to describe how we achieved the integration in order
to test our hypothesis, and we intend that the material and methods
section, along with the model code itself, will help others to carry
out similar studies. However, we wish to devote the majority of this
discussion to what can be learned from an integrated model of a
combined brain and biomechanical system, using our oculomotor system
as an example.

@@

@@

\subsection{Concluding remarks}

@@

% Significance of this work.
This work represents a step forward in the modelling of neuromuscular
systems, not because it significantly advances any of the constituent
models, but because it \e{integrates} the models into a
complete, \e{behaving} system.  This is not the first integrated brain
model composed of separately developed components. The works
of \cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are both based
on an example of a brain model which drives a simple, second order
model of the eye. \cite{dewolf_spiking_2016} describes a reach model
which integrates models of cortex and cerebellum to drive a two
degree-of-freedom arm model. Both of these example systems
nevertheless operate using `curated' inputs supplied by the modeller.

In contrast, the current work allows the state of the system to
determine the input delivered to the model. The modeller only curates
the state of the world at each time point, but the actual input to the
model depends on the eye's rotational state.  This is, to our
knowledge, the first model which integrates the brain with an accurate
biophysical system and closes the loop in this way, enabling the
system to reproduce behaviour.  As such, it offers a platform for
testing more complex saccadic behaviour such as antisaccades or
saccades in the presence of distractor stimuli. We believe that by
building closed loop systems which express behaviour, we, and others
will develop a new field of \e{computational neurobehaviour}, which
will share themes from neuroscience, artificial intelligence, decision
science and embodied robotics.

>>>>

% Brain to SBG, seeing as that's how I explained it above.
A number of studies have considered the form of the connection between
the deeper layers of the superior colliculus and the saccadic burst
generator \citep{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_two-dimensional_1994,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
which has become known as the spatial temporal transform (STT).  The
spatial aspect of the transform is thought to be implemented by a
weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994}.
\rvwt{Although there is no definitive experimental proof for such a mapping,
there exists evidence for spatially variable synapse
density \citep{moschovakis_anatomical_1998,herrero_influence_1998} and
connection density \citep{grantyn_density_2002} and we therefore adopt
the idea.}
%
Arai and co-workers trained a 20x20 neural network model of the
superior colliculus to discover the weight map under the assumption of
2D Gaussian activation
profiles~\citep{arai_two-dimensional_1994}---\rvwt{that is, they
assumed that the activity in superior colliculus for any saccade was a
size-invariant 2D Gaussian hill of activity}.
%
The training approach of \cite{arai_two-dimensional_1994} was not
feasible in this study due to the length of time required to run our
model and its stochasticity, which meant multiple runs of the model
were necessary in order to generate output statistics.
%
\cite{tabareau_geometry_2007} wrote down a theoretical form of the weight
map, \rvwt{obtained by inverting the mapping} of \cite{ottes_visuomotor_1986}
and the assumption of invariant 2D Gaussian activity profiles in SC,
\rvwt{which is equivalent to:}
%
\begin{equation} \label{eq:tabareau_eq3}
w(r,\phi) = i\;e\,^{jr}\;\sin\left(l\phi + k\right)
\end{equation}
\rvwt{where $r$ and $\phi$ are co-ordinates on the collicular map and
$i$, $j$, $k$ and $l$ are parameters of the
function (compare with Eq.~3 of \cite{tabareau_geometry_2007}).}
%
As they found it closely resembles the results
of \cite{arai_two-dimensional_1994}, and it is a simple formulation,
we considered it as the means to generate the six weight maps in our
own model.
%
One barrier to the use of this weight map was the \ccg~model's
violation of the
\e{invariant integral hypothesis}. This states that the number of spikes
emitted by a neural element during a saccade (or in our model, the
integral of the neuron's output during the saccade) should be a
function only of its position within the hill of collicular
activity. That is, for any time-dependent hill of activity
$\mathcal{A}(\mathbf{z},t)$ at $\mathbf{z} = (r,\phi)$ on the collicular
surface, the integrated activity  $A_{\mathbf{x}}$ in an element at a
vector $\mathbf{x}$ away from $\mathbf{z}$ is
\begin{equation}
A_{\mathbf{x}} = \int_t \mathcal{A}(\mathbf{z}-\mathbf{x}, t)\;dt
\end{equation}
which is invariant for all $\mathbf{z}$. \rvwt{This requirement is
fulfilled by spatially invariant 2D Gaussian profiles, whose
time-course (how quickly they grow and then diminish) is always the
same.}

@@

A further issue regarding the use of the theoretical weight map
in \cite{tabareau_geometry_2007} was that it does not consider the
existence of the oblique extraocular muscles. There is evidence that
only two dimensional information is encoded in superior
colliculus
\citep{wurtz_activity_1972,hepp_monkey_1993,van_opstal_two-rather_1991},
but the eye is actuated by six extraocular muscles. In order to find
out a possible form for the input to the oblique muscles we carried
out a training process
% possibly descibe this training process in supplemental data
which depended on a centroid computation in SC\_deep and was designed
to maintain a null torsional eye rotation for all saccade
end-points. For the four rectus muscles, the resulting weight map
solutions resembled those found by
\cite{arai_two-dimensional_1994}. The trained
maps for the oblique muscles had a form very close to those for the
inferior and superior rectus channels, but with a smaller magnitude.
The inferior oblique map resembled the superior rectus map and the
superior oblique map resembled the inferior rectus. When parameterising
the theoretical weight maps, we set the inferior/superior
oblique maps to be 1/10$^{\mathrm{th}}$ of the superior/inferior rectus
maps, respectively. Interestingly, this suggests that there is a built-in
synergy between the vertical and oblique channels in the eye, although
the results will show there is some systematic change in the oblique error
with saccade end-point location.
% Could elaborate here on Listings Law, and why I didn't train to
% Listings Law. Do this in the chapter, rather than here in the paper.

@@

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:results:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{fig:saccvstarg}(a) \& \rvw{(b)}. We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$.

The resulting weight maps (where the oblique maps are
1/10$^{\mathrm{th}}$ of the vertical maps, as described earlier) are
shown in Fig.~\ref{fig:weightmaps}.
%
\rvw{First, recall that the $r$ axis of the neural surface corresponds
to the amplitude of a saccade and the $\phi$ axis indicates the polar
direction of the saccade, as described in Sect.~\ref{sec:mapping} and
Fig.~\ref{fig:mapping}. Fig.~\ref{fig:weightmaps}(a) shows the weight
map for the muscle which rotates the eye to the left. As we modelled a
left eye, this actuates the lateral rectus muscle. The exponential
rise of Eq.~\ref{eq:weightmaps} [for experimental evidence,
see Figs.~7 \& 8 of \cite{herrero_influence_1998}] is seen in the
$r$ direction; as $r$ increases, so the connection strength to the SBG
channel rises exponentially. The connection strength is greatest along
the centre line, for a value of $\phi$ which corresponds to a purely
leftward movement. Note that $\phi$ is presented in neural
coordinates, and not in degrees or radians; 1$\leq\phi\leq$50
corresponds to a range of 0\dg~to 360\dg; $\phi=$38.5 corresponds to
movements left. The connections strength drops away sinusoidally as
$\phi$ moves away from the centre line at $\phi=$38.5. In regions of
the map for which there is no leftward movement, that is, in the half
of the map which corresponds to any movement with a rightward
component, the `left' weight map is 0. Fig.~\ref{fig:weightmaps}(d)
shows the weight map for rightward movements, actuating the medial
rectus muscle of the eye. The line of maximum connection strength is
along $\phi=$13.5. The map is a mirror of
Fig.~\ref{fig:weightmaps}(a), reflected about the line $\phi$=26. The
`left' and `right' weight maps are orthogonal; the non-zero region of
the `left' map is zero in the `right' map and vice
versa. Fig~\ref{fig:weightmaps}(b) \& (d) show the weight maps for
downward and upward eye movements; the `down' map activates the SBG
channel for the inferior rectus muscle, the `up' map activates the
superior rectus. Note that `down' is not orthogonal either to `left'
or `right' because a saccade down and left is achieved by
simultaneously activating both the lateral and inferior rectus
muscles. However, the `up' map \e{is} orthogonal to the `down' map and
spans the edges of the surface where $\phi$ rolls over from 1 to
50. The line of maximum connection strength for the `up' map is along
$\phi=$1; for `down' $\phi=$26. Based on the training described in
Sect.~\ref{sec:methods:integrating}, the maps driving the superior
oblique (`Z+') and inferior oblique (`Z-') muscles were set to
1/10$^{\mathrm{th}}$ of the `down' and `up' maps.}
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

@@

To verify that our implementation of the brain model has the same
functionality as that reported in \cite{cope_basal_2017}, we
investigated the effect on saccadic response times of: target
eccentricity; and any gap or overlap between fixation off-time and
target on-time. We showed that the full model reproduces the `hockey
stick' shape shown in Fig. 7 of \cite{cope_basal_2017} and discovered in
experimental data \citep{reulen_latency_1984} for horizontal
[Fig.~\ref{fig:latvsall}(a)], vertical [Fig.~\ref{fig:latvsall}(b)] and
oblique saccades (not shown). The latency increases with eccentricity
far from the fovea because the retinotopic mapping reduces the
activity in the basal ganglia for more eccentric targets (see
Fig.~\ref{fig:mapping}). Closer to the fovea, the \rvwt{effect of} the
foveal mask \rvwt{on} the activity in FEF again leads to reduced input
into the basal ganglia and an increased time to achieve disinhibition
in SNr.

@@

The aim of this study was to demonstrate the importance of modelling
neurological systems \e{in concert with} the biomechanical systems
with which they have evolved. We hypothesised that by
combining existing neurophysiological models with an accurate model of
a musculo-skeletal system, and then \rvw{closing the
`agent-environment-agent' loop} by allowing the
movements of the virtual muscles to modulate sensory feedback to the
brain model, shortcomings in the constituent models would be revealed,
leading to new knowledge.

To demonstrate the validity of this closed-loop
approach, we built an integrated model and then identified the
modifications which were necessary to give it the ability to make
accurate movements under one type of stimulus. We then examined its
behaviour with other stimuli. We chose the oculomotor model as a basis
for this study because it has only three degrees of freedom, making it
one of the simplest musculo-skeletal systems. Furthermore, eye
movements fall into several well-defined categories, each being
controlled by separate brain circuits, we were therefore justified in
modelling a system which produced only saccadic eye
movements. Nevertheless, we are aware that we did not create a
complete model of the system; no treatment of the cerebellum was
attempted, justified because cerebellum appears to have only a minor
effect on saccade accuracy \citep{dean_adaptive_2008}, probably
correcting for slow to medium timescale changes in the physical
dynamics of the eyeball \citep{dean_learning_1994}.

To summarise our model integration: We combined
the \ccg~model \citep{cope_basal_2017} with a saccadic burst generator
model based on the work of \cite{gancarz_neural_1998}, using this to
drive the input of a new biomechanical eye model. To achieve the
spatial transformation from the retinotopic maps of the \ccg~model to
the six `muscle channel' inputs for the saccadic burst generator, we
used the mapping of \cite{ottes_visuomotor_1986} to produce
parameterised weight maps along with an empirically discovered synergy
for the torsional weight maps. We introduced an additional
transformation to the brain model to achieve invariant sized hills of
activity in superior colliculus to fulfil the invariant integral
hypothesis of \cite{tabareau_geometry_2007}. We closed the loop using
a software component which transformed a view of a world containing
luminous cross shapes into the eye's frame of reference, given its
instantaneous rotational state. This component also computed the
inverse of the mapping from \cite{ottes_visuomotor_1986} to project
the view retinotopically into the brain model.
%
This paper serves to describe how we achieved the integration in order
to test our hypothesis, and we intend that the material and methods
section, along with the model code itself, will help others to carry
out similar studies. We will discuss what can be learned from an
integrated model of a combined brain and biomechanical system, using
our oculomotor system as an example and then consider how this study
compares with other modelling and robotic studies of closed-loop
systems.

@@

%
% A couple of last points to round up the discussion of THIS model
%

@@

@@

\subsection{Comparison with other studies}

\rvw{We have called this closed-loop, biomimetic modelling approach \e{computational
neurobehaviour}, in which a complete, behaving model is constructed,
with attention paid to the biological accuracy of each brain and
biomechanical sub-system. There already exist many
closed-loop \e{robotic} systems which receive sensory input from the
world, process that input and generate behaviour by activating motor
systems
\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
now consider whether robotic systems which model biological
components \e{in hardware} could fall within our new category.
%
Using a number of examples, we will attempt to illustrate what we mean
by computational neurobehaviour. We'll consider which examples fall
into the new category and which are covered by other fields of
robotics or computational neuroscience.}

\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
biomimetic whisker sensory system, along with a biomimetic neural
system imitating the operation of the rat's sensory processing and
controlling the movement of the robot. \cite{fend_artificial_2004} is
a similar, wheeled, whiskered robot, with a repertoire of three
behaviours organised in a subsumption architecture. In both robots,
actions that are selected within the brain model drive a
non-biologically accurate wheel motor control algorithm to achieve
rotational and translational movements. Although both have sensory and
processing systems which are guided by biology, the non-biological
motor control stage prevents us from considering these as being
studies of computational neurobehaviour. Instead, we would refer to
these as \e{embodied models}, as described
in \cite{bolado-gomez_biologically_2013}, a study in which the
learning behaviour of a biomimetic `core' model is embedded within an
engineered `architecture' (a wheeled robot) which closes the
agent-environment loop.}
%
\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
whose motor system closely resembles that of the real fish. The robot
is able to operate in a closed-loop mode, where sensory input is
provided to the non-biomimetic control algorithms from overhead
cameras, but its control system is also able to operate in open-loop
mode. Neither the control system, nor the sensory system are
biophysically accurate and we would not describe this study as
computational neurobehaviour. Nevertheless, the biophysically accurate
motor system they describe has the potential to form part of a
computational neurobehavioural study of swimming behaviour in the
fish, if it were combined in a loop with suitable sensory input and
sensory processing models.}
%
\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
arm controlled via a dynamic neural field brain model. The sensory
input for this system---its `eyes'---is a Microsoft Kinect sensor; it
also has somatosensory feedback from the fingers of the robot's
hand. The neural field `brain' controls the seven degrees of freedom
of the arm to carry out the reach-and-grasp action. While this robot
has closed-loop control and is clearly inspired by biology, it remains
a study of robotics and of the improvement of the control of the
robot's reach-and-grasp function, rather than a study which aims to
learn more about the biology of a primate arm. For this reason, we
would describe the study of \cite{knips_neural_2017} as an embodied
model.}

\rvw{To summarise, in most closed-loop robotic studies which
incorporate neuro-mimetic models, the hardware forms an `engineered
surround architecture', allowing for the examination of the behaviour
of the embodied model. However, suitably \e{biomimetic} hardware such as
the fish in \cite{yu_development_2004} would not be excluded from
computational neurobehavioural studies.}

\rvw{Modern programming platforms, often originating from the
computer game industry, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuro-mimetic control are carried out with virtual robots
operating within a virtual environment.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control \e{and} motor output in
software. These studies fall outside the remit of computational
neurobehaviour only because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewer degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a computational
neuroscience study of a (virtually) embodied model.}
%

%
% Now the closing section of the discussion.
%

\rvw{Thus, while there are many models that close the
agent-environment loop and display partial biological plausibility,
the biomimetic features are usually confined to a sub-system of the
entire model. This leads us to formalise a definition of computational
neurobehaviour as: \e{The study of biological sensory-motor system
behaviour using biologically accurate models of sensory input, brain
and motor sub-systems operating in a closed-loop}.}
%
% Another computational neurobehavioural study?
\rvw{We believe our oculomotor model is one of the first such models
using this approach and shares many features with that
of \cite{arena_motor-skill_2017} which describes a robotic insect
system based on the fly species \e{Drosophila Melanogaster}. It has
biomimetic insect legs implemented in a virtual robot and a
neuro-mimetic brain. Closing the loop is a visual sensory input system
which is able to determine the distance between the robot and an
obstacle and the obstacle's height. The authors demonstrate that the
virtual robot is able to learn to climb obstacles in a realistic
manner and suggest that the model may be compared with experimental
data from future Drosophila experiments addressing obstacle climbing
and learning. The visual system is not described in detail, but if it
is modelled in a biologically plausible manner, then this work may
reasonably be described as a computational neurobehaviour study,
contemporaneous with our own.}

% Significance of this work.
%% This work represents a step forward in the modelling of neuromuscular
%% systems, not because it significantly advances any of the constituent
%% models, but because it \e{integrates} the models into a
%% complete, \e{behaving} system.  This is not the first integrated brain
%% model composed of separately developed components. The works
%% of \cite{nguyen_saccade_2014} and
%% \cite{thurat_biomimetic_2015} are both based
%% on an example of a brain model which drives a simple, second order
%% model of the eye. \cite{dewolf_spiking_2016} describes a reach model
%% which integrates models of cortex and cerebellum to drive a two
%% degree-of-freedom arm model. Both of these example systems
%% nevertheless operate using `curated' inputs supplied by the modeller.

%% In contrast, the current work allows the state of the system to
%% determine the input delivered to the model. The modeller only curates
%% the state of the world at each time point, but the actual input to the
%% model depends on the eye's rotational state.  This is, to our
%% knowledge, the first model which integrates the brain with an accurate
%% biophysical system and closes the loop in this way, enabling the
%% system to reproduce behaviour.  As such, it offers a platform for
%% testing more complex saccadic behaviour such as antisaccades or
%% saccades in the presence of distractor stimuli. We believe that by
%% building closed loop systems which express behaviour, we, and others
%% will develop a new field of \e{computational neurobehaviour}, which
%% will share themes from neuroscience, artificial intelligence, decision
%% science and embodied robotics.
